\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd
Flowchart

@@

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

>>>>

---
nocite: |
  `r cite_r("r-references.bib")`
---

@@

```{r flowchart }
Flowchart1 <- grViz("digraph nicegraph{

                    graph [layout = dot,fontsize = 14]

                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, fixedsize = true]

                    A[label = '48 items were generataed by a robust expert panel'] 
                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']

                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, fixedsize = true]
                    C[label = 'Factor Identification
                    Scree Plot: 6 Factors
                    Parallel Analysis: 6 Factors
                    Minimum Average Partial Method: 5 Factors
                    Hull Method: 5 Factors']

                     subgraph cluster_1 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]

                     1[label = '5 Factor Solution Retained 23 Items']
                     2[label = 'Reliability Analysis on EFA Sample (N=428)
                    Alpha F1 =.49; F2 = .71; F3 = .86; F4 =.62; F5 =.77']

                     3[label = 'Confirmatory Factor Analysis on Modified Model
                     on the Five Factor Model (21 Items; N=199)
                      Acceptable Fit ( CFI = .92; TLI .91; RMSEA = .05, SRMR = .07)']

                     4[label = 'Reliability Analysis on CFA (N=199) 
                      Alpha F1=.47; F2=.67; F3 =.92; F4=.58; F5= .74']
                    }
                subgraph cluster_2 {
                      graph[shape = rectangle]
                      style = rounded
                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
                    5[label = '6-Factor  one factor with only two salient loadings']
                    6[label = 'Rejected']
                    }

                     edge[color = black,arrowhead = vee, arrowsize = 1.25]
                     A ->B
                     B ->C
                     C ->1
                     1 ->2
                     2 ->3
                     3 ->4
                     C ->5
                     5 ->6

}")

export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  png::writePNG("Flowchart1.png")

```{r, out.height= "50%",  fig.align='center', fig.cap='ABC'}
knitr::include_graphics('Flowchart1.png')
```

## Procedure
Our study had three objectives. First, to develop an instrument to assess individual's light exposure behavior . Second, to conduct an exploratory factor analysis to understand the latent structure. Third to gather validity evidences [@furrPsychometricsIntroduction2014].

## Data analysis
